\documentclass[11pt,letterpaper]{article}

\input{aliases}
\input{cvstyle}
\input{pubs_summary_macros}

\usepackage{fontawesome5}
\newcommand{\makefield}[2]{\makebox[1.5em]{#1} #2}

\addtolength{\topmargin}{-0.2in}
\addtolength{\textheight}{0.4in}
\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{0.4in}

\begin{document}\thispagestyle{empty}\sloppy\sloppypar\raggedbottom

\textbf{\Large \fullname} \\[0.5ex]
\currentposition \\[1.0ex]
\textsf{\small 
    \makefield{\faMapPin}{\address} %
    \makefield{\faEnvelope[regular]}{\href{mailto:\email}{\texttt{jpdeleon[at]g.ecc.u-tokyo.ac.jp}}}\\%
    \makefield{\faPhone}{\url{\phonenumber}} %
    \makefield{\faBook}{\href{\scholarurl}}{Google scholar} %
    % \href{\orcidurl}{ORCID: \orcid} | %
    \makefield{\faLinkedin}{\href{\linkedinurl}{\texttt{linkedin.com/in/jpdeleonbsap}}}\\%
    \makefield{\faGlobe}{\url{\githuburl}} %
}\\[0.5ex]


\subsection{Overview}
Data scientist and astrophysicist with 5+ years of experience building complex data analysis pipelines, statistical models, and scientific software. Proven track record of leading international research projects, analyzing large-scale time-series datasets from NASA's space telescopes, and delivering reproducible insights using modern probabilistic programming frameworks. Strong background in Bayesian inference, optimization, and mentoring cross-functional teams.

\subsection{Skills}
\begin{list}{}{\cvlist}
    \item \textbf{Programming \& Scientific Computing:} 
    Python (NumPy, SciPy, Pandas, JAX, NumPyro); experience in building complex data analysis pipelines for large temporal and spatial datasets    
    \item \textbf{Data Analysis \& Modeling:} 
    Time-series analysis, Bayesian inference, probabilistic modeling, optimization, statistical analysis of large survey data, technical writing, project management
    \item \textbf{Software \& Systems:} 
    Linux/Unix environments, server administration (Grafana monitoring), Bash scripting, version control (Git), automation, reproducible research workflows
    \item \textbf{Visualization \& Communication:} 
    Matplotlib, scientific visualization, academic writing, conference presentations, public outreach
    \item \textbf{Leadership \& Mentorship:} 
    Research group supervision, student advising (PhD, MSc, undergraduate), curriculum design, international collaboration
    \item \textbf{Languages:} 
    Filipino (native), English (fluent), Japanese (working proficiency)
\end{list}

\subsection{Full-time Positions}
\begin{list}{}{\cvlist}
    \item
        \textbf{Project Assistant Professor (2025/4 - Present)} \\
        \textit{Komaba Institute for Science, Graduate School of Arts and Sciences, The University of Tokyo, Japan} \\
        \textit{Role: Management of observations and data analysis with \href{\muscatLCOurl}{MuSCAT4} under the \href{\kibanSurl}{Kiban S} project.}\\
        
    \item
        \textbf{Project Research Assistant (2023/4 - 2025/3)} \\
        \textit{Department of Multi-Disciplinary Sciences, Graduate School of Arts and Sciences, The University of Tokyo, Japan} \\
        \textit{Role: Spearheading the discovery and in-depth characterization of young transiting exoplanets using the TESS telescope.}
        \textit{Advisor: \href{\naritaurl}{Prof. Norio Narita}} (Refer to \href{\paperthree}{de Leon et al. 2023})\\

    \item
        \textbf{Project Research Assistant (2021/4 - 2023/3)} \\
        \textit{Department of Astronomy, Graduate School of Science, The University of Tokyo, Japan} \\
        \textit{Role: Led an international group of astronomers towards the discovery of 37 new transiting exoplanets using the Kepler telescope.}
        \textit{Advisor: \href{tamuraurl}{Prof. Motohide Tamura}} (Refer to \href{\papertwo}{de Leon et al. 2021})\\
        
    \item
        \textbf{Research Development Assistant (2013/4-2014/6)}\\
        \textit{Regulus SpaceTech, Inc., Los Ba\~nos, Laguna, Philippines}\\
        \textit{Role: Initiated the software development for automating solar telescope control and data analysis.}
        \textit{Advisor: \href{\seseurl}{Dr. Rogel Sese}} \\
\end{list}

\subsection{Temporary Positions}
\begin{list}{}{\cvlist}
    \item
        \textbf{Remote Lecturer (2021/6 - 2021/10)} \\
        \textit{Faculty of Aerospace Engineering, School of Engineering \& Architecture, Ateneo de Davao University, Philippines} \\
        \textit{Role: Crafted and conducted lectures on Introduction to Astronomy \& Astronomical Data Analysis.}
        
    \item 
        \textbf{Technical Assistant (2018/10-2019/3)}\\
        \textit{Engineering Department, The University of Tokyo, Japan}\\
        \textit{Role: Developed innovative image processing software for stitching featureless high-resolution images 
        \textit{Advisor: \href{hayakawaurl}{Assoc. Prof. Tomohiko Hayakawa}} (Refer to \href{\spieurl}{Murakami et al. 2018})}

    \item 
        \textbf{Research Assistant (2017/4-2018/3)}\\	
        \textit{Department of Astronomy, The University of Tokyo, Japan}\\
        \textit{Role: Developed a robust pipeline for modeling and analyzing multi-wavelength transit light curves and provided mentorship to new research group members.}

    \item 
        \textbf{Research Student (2015/9-2016/3)}\\
        \textit{Department of Astronomy, Graduate University for Advanced Studies (SOKENDAI), Japan}\\
        \textit{Role: Worked on data reduction and analysis of high-resolution astronomical images and contributed to scientific report writing.}
        \textit{Advisor: \href{\mayamaurl}{Dr. Satoshi Mayama}} \\

    \item 
        \textbf{Intern (2014/7-2014/9)}\\
        \textit{Academia Sinica Institute for Astronomy and Astrophysics (ASIAA), Taipei, Taiwan}\\	
        \textit{Role: Developed an image processing pipeline for the analysis of high-resolution images of a young forming star using the 8-m Subaru telescope.}
        \textit{Advisor: \href{takamiurl}{Dr. Michihiro Takami} (Refer to \href{\paperone}{de Leon et al. 2015})} \\
\end{list}

\subsection{Education}
\begin{list}{}{\cvlist}
    \item
        \textbf{PhD, 2021} Department of Astronomy, The University of Tokyo, Japan.\\
        Title: Discovery and Characterization of Transiting Exoplanets with Diverse Radii and Ages (\href{\phdthesisurl}{online version}).
        Advisor: \href{\tamuraurl}{Prof. Motohide Tamura}
    \item
        \textbf{MSc, 2018} Department of Astronomy, The University of Tokyo, Japan.\\
        Title: Multi-color Simultaneous Transit Observations of Low Density Hot Jupiters (\href{https://github.com/jpdeleon/thesis-master/tree/master}{online version}).
        Advisor: Prof. Motohide Tamura
    \item
        \textbf{BSc, 2013}\\
        Department of Physics, University of the Philippines, Los Ba\~nos, Laguna, Philippines.\\
        Title: Thermal Differential and Image Analysis of a Fabricated 11-cm Solar Telescope using an Active-Passive Cooling System.
        Advisor: \href{\seseurl}{Dr. Rogel Mari Sese}      
\end{list}

\subsection{Awards}
\begin{list}{}{\cvlist}
    \item \textbf{2022/12:} St. Joseph's Academy, Centennial Achiever's Award
    \item \textbf{2021/3:} Philippine Embassy in Japan, Medal for distinguished Filipino Graduates
    \item \textbf{2018/4-2021/3:} Ministry of Education, Culture, Sports (MEXT) PhD Scholarship (JPY 8.4M)
    \item \textbf{2016/4-2018/3:} MEXT MSc Scholarship (JPY 5.6M)
    \item \textbf{2015/4-2016/3:} MEXT Japanese Language and Research Scholarship (JPY 2.8M)
    \item \textbf{2015/10-2016/3:} Research Grant from the Graduate University for Advanced Studies (JPY 0.2M)
    \item \textbf{2014/9:} SanDisk Japan Scholarship (USD 3.75k, deferred)
    \item \textbf{2013/3:} International Space University Scholarship (EUR 9k, deferred)
    \item \textbf{2011-Present:} Received multiple travel grants to attend workshops in the US and Taiwan related to data science, and participated in research-related conferences and observation runs in the U.S., Europe, South Africa, and South-east Asia
\end{list}

\subsection{Teaching and Mentorships}
\begin{list}{}{\cvlist}
    \item \textbf{Designed and Taught Courses:} Created and delivered two elective courses for 4th-year undergraduate Aerospace Engineering students at the \href{http://sea.addu.edu.ph/programs/aerospace-engineering/}{Ateneo de Davao University} during the 2nd semester of 2021.
    \item \textbf{Research Collaborations:} Collaborated with M. Mori (Current postdoc) on the discovery and validation of a rare planet in the Neptune desert (Refer to \href{https://ui.adsabs.harvard.edu/abs/2022AJ....163..298M/abstract}{Mori et al. 2022}).%; \href{https://github.com/jpdeleon/toi1696}{github.com/jpdeleon/toi1696}).
    \item \textbf{Pipeline Development:} Wrote a public Python code for easily analyzing data from TESS telescope appropriate for research and instruction (Refer to \href{https://github.com/jpdeleon/quicklook}{github.com/jpdeleon/quicklook})
    \item \textbf{Thesis Advisory:} Worked with H. Kobayashi (Former undergraduate student) to develop a pipeline for finding young transiting planets and binary stars in nearby star clusters (Refer to \href{https://github.com/hiremasa/ytps}{github.com/hiremasa/ytps}). Also advised A. Nodado (Former student) on her undergraduate thesis focused on Mira variables.
    \item \textbf{MEXT Scholarship Guidance:} Provided guidance to A. Javier and C. Cabatlao from their scholarship application to acceptance, supporting their successful pursuit of graduate studies in Japan.
\end{list}

\subsection{Trainings and Workshops}
\begin{list}{}{\cvlist}
    \item Nature Masterclasses: Impressive Academic Presentations (Expert trainer-led full-day workshop), University of Tokyo, March 18, 2026
    \item University of Tokyo Faculty Development (\href{https://utokyofd.com/en/ffdp/about/}{UTokyo FD Open}) Program, Tokyo, Japan, Oct 2025--Feb 2026
    \item \href{https://www.exoclock.space/annual_meetings}{5th ExoClock Meeting}, Madrid, Spain, Oct 4--6, 2025
    \item \href{https://eventos.upm.es/132958/detail/ariel-consortium-meeting-madrid.html}{ARIEL Consortium Meeting}, Madrid, Spain, Sep 30--Oct 4, 2025
    \item \href{https://sites.google.com/g.ecc.u-tokyo.ac.jp/young-transiting-planet-worksh/home}{Young Transiting Planet Workshop 2025}, Ishigaki, Japan, Mar 12--15, 2025
    \item \href{https://indico.narit.or.th/event/203/}{JWST Data Analysis Workshop}, Chiang Mai, Thailand, Jun 24--Jul 5, 2024
    \item Japan Planetary Atmosphere Research Society Workshop II, Atami, Japan, Mar 2023
    \item Japan Planetary Atmosphere Research Society Workshop, Matsushima, Miyagi, Japan, Mar 2022
\end{list}

\subsection{Outreach Activities}
\begin{list}{}{\cvlist}
    \item Resource speaker for Junior High School Career Week, SJASQ, Philippines, Jan 24, 2026
    \item Guest on a podcast titled ``Are We Alone?'' (published on \href{https://open.spotify.com/episode/2hfoLrrP6TKyKE7mgu6pju?trackId=7BRD7x5pt8Lqa1eGYC4dzj}{Spotify}), Dec 2025
    \item Resource speaker for Philippine Astronomy Week 2024 led by PAGASA, Philippines, Feb 2024
    \item Featured by Pinoy Scientists (\href{https://www.facebook.com/pinoyscientists/posts/pfbid0Lj83pJZaaU35tdSpz5UKgkAodhBqMzudUjCS7z4UV32zqiqmkQzT7LdtpGTsu7Cql}{Jan 2023})
    \item Resource speaker for Science Week at De La Salle Integrated School, Philippines, Mar 2022
    \item Resource speaker for the Philippine Science High School--Western Visayas Campus, Philippines, Mar 2021
    \item Courtesy call with the Director of the Philippine Space Agency (PhilSA), Mar 2021
    \item Invited speaker at the National Institute of Physics, University of the Philippines Diliman (UPD), Jan 2020
\end{list}

\subsection{Affiliations and Services}
\begin{list}{}{\cvlist}
    \item Monthly Notices of the Royal Astronomical Society (\href{https://academic.oup.com/mnras}{MNRAS}; Impact Factor: 4.8; active referee)
    \item SPACETIDE Foundation (\href{https://spacetide.jp/en/}{spacetide.jp}; active intern, 2022--present)
    \item Science Integrated Direction for High School Investigators (\href{https://www.sidhi.org/}{SIDHI}; mentor, 2022--present)
    \item Science and Technology Advisory Council--Japan Chapter (\href{https://www.facebook.com/profile.php?id=100083271798519}{STAC-J}; member, 2019--present)
    \item Exoplanet Follow-up Observing Program (\href{https://exofop.ipac.caltech.edu/tess/}{ExoFOP}; member, 2018--present)
\end{list}

\end{document}
